---
title: "Data Import"
output: github_document
---
this is the respository for data wrangling 1 part of P8105

```{r setup}
library(tidyverse)
library (readxl)
library (haven)
```

##Read in some data

Read in the litters data set and re name it. This document will show how to import data.

#Import the FAS Litters CSV
```{r}
litters_df = read_csv(file = "./data_import_examples/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
```
##Take a look at the data
Printing in the console
```{r}
litters_df
```
```{r}
tail(litters_df)
```
```{r}
skimr::skim(litters_df)
```


## Options to read_csv
checkout '?read_csv() for more information.

## Other file formats
Read in an excel file.

```{r}
mlb_df = read_excel("./data_import_examples/mlb11.xlsx", range = "A1:F7")
mlb_df
```

Read in a SAS file

```{r}
pulse_df = read_sas("./data_import_examples/public_pulse_data.sas7bdat")
```

## Comparison with Base R
What about read.csv?
```{r}
litters_base = read.csv("./data_import_examples/FAS_litters.csv")
litters_readr = read.csv("./data_import_examples/FAS_litters.csv")
```

## Exporting data
Export the mlb sub table
```{r}
write_csv(mlb_df,"./data_import_examples/mlb_subtable.csv")
```


#Import FAS Pups File
pups_df = read_csv(file = "./data_import_examples/FAS_pups.csv")
pups_df = read_csv(file = "~/Desktop/Data Science 1/data_wrangling_1/data_import_examples/FAS_litters.csv")





